%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
\section{Introduction}

With the rise of Large Language Models (LLMs) and the increase
in their capabilities, companies are motivated to use LLMs for
automation tasks, including testing and its tooling. However, LLMs
are not plug-and-play; specialized tooling is often required to
produce reliable outputs.
This work defines a formal base into which LLMs rewrite requirements
and test cases written in natural language, so that the result is
parsable by coverage checking systems.

There is an increasing demand to instrument systems in natural
language, including the specification of requirements and their
test cases for testing systems and system components. Even when
requirements and test cases are written in English, they must
still be rewritten into a mathematical formal base so that existing
test-coverage techniques can be applied. A formal
base into which LLMs can convert human-written text is therefore
needed. This formal base must be able to express all motivational
requirement examples. Its semantics must be easily interpretable
by LLMs and agentic systems, so that agents can rewrite requirements
and test case descriptions from human language into the formal base
with high accuracy and without changing the semantics; the formalism
itself must be unambiguous. It must also be convertible to existing
formal bases used by formal verification methods. A good formalism
should meet all of the mentioned criteria.

%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
\section{How To Use This Template}

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{What Files are Here and Why}

%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
\section{How To Write the Paper --- A Few Hints}

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Images and Tables}

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Sections and Subsections}

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Keywords}

%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
\section{Some Useful Tools}

%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
\section{Frequently Used \LaTeX{} Fragments}
%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
%--------------------------------------------------------
\section{Conclusions}
\label{sec:Conclusions}

\textbf{[Paper Summary]} What was the paper about, then? What the reader needs to remember about it?

\textbf{[Highlights of Results]} Exact numbers. Remind the reader that the paper matters.

\textbf{[Paper Contributions]} What is the original contribution of this work? Two or three thoughts that one should definitely take home.

\textbf{[Future Work]} How can other researchers / developers make use of the results of this work?  Do you have further plans with this work? Or anybody else?

\section*{Acknowledgements}
I would like to thank my supervisor X. Y. for his help.